\documentclass[a4paper,11pt]{article}

\usepackage{url}
\usepackage{parskip}

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}

\usepackage{enumitem}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\setlength\bibitemsep{1em}

\usepackage{fontawesome5}

\newenvironment{jobshort}[2]
{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & #2 \\[3.75pt]
    \end{tabularx}
    }
    {
}

\newenvironment{joblong}[2]
{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=\textbullet]
        }
        {
        \end{itemize}
    \end{minipage}
}

\begin{document}

    \pagestyle{empty}

    \begin{tabularx}{\linewidth}{@{} C @{}}
        \Huge{Md. Mosfikur Rahman} \\[7.5pt]
        \href{https://github.com/mdmosfikurrahman}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \
        \href{https://linkedin.com/in/mdmosfikurrahman}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \
        \href{https://mdmosfikurrahman.github.io}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \
        \href{mailto:mdmosfikurrahman.cse@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ mdmosfikurrahman.cse@gmail.com} \ $|$ \
        \href{tel:+8801332512922}{\raisebox{-0.05\height}\faMobile \ +8801332512922} \\
    \end{tabularx}

    \section{\textbf{Work Experiences}}

    \begin{joblong}{Software Engineer, REVE Systems Ltd.}{July 2023 - Present}
        \item Optimize data structures in Oracle DB for efficient storage and retrieval.
        \item Research and integrate new tools, libraries, APIs, and frameworks for enhanced performance.
    \end{joblong}

    \begin{joblong}{Software Engineer, BJIT Group}{April 2022 - June 2023}
        \item Implement JavaEE back-end/API using REST, SOAP, Spring, and microservices.
        \item Create fundamental design documents, including API specifications and UMLs.
    \end{joblong}

    \begin{joblong}{Trainee Software Engineer, BJIT Group}{October 2021 - March 2022}
        \item Assisted in coding, debugging, and testing while learning industry best practices.
        \item Developed skills in JavaEE, REST, SOAP, Spring, and front-end technologies.
    \end{joblong}


    \section{\textbf{Skills}}
    \begin{tabularx}{\linewidth}{@{}l X@{}}
        Programming Languages & \normalsize{Java, JavaScript, Python}                                               \\
        Frameworks            & \normalsize{Spring Boot, Spring Batch, Bootstrap, Thymeleaf, React JS}              \\
        Database Expertise    & \normalsize{Oracle, MySQL, MongoDB, Spiral DB}                                      \\
    \end{tabularx}

    \section{\textbf{Education}}
    \begin{tabularx}{\linewidth}{@{}l X@{}}
        2021 & Bachelor of Science (B.Sc.) in Computer Science and Engineering \newline \textbf{Daffodil International University, Bangladesh} \hfill (CGPA: 3.83/4.00) \\

        2021 & Exchange Program in Computer Science and Engineering \newline \textbf{Adam Mickiewicz University, Poland} \hfill (Passed with 80\% Marks)             \\
    \end{tabularx}

    \section{\textbf{Projects}}
    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Customs Bond Management System, NBR} & \hfill \textit{\href{https://cusbond.gov.bd/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Acted as the module owner including Legal and Case Information System, Utilization Declaration System.
                \item Implemented BGMEA and BKMEA Database integration for Utilization Declaration.
            \end{itemize}
        } \\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Rakuten Echiba Backend Development, Rakuten} & \hfill \textit{\href{https://www.rakuten.co.jp/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Solely focused on backend development for the Rakuten Echiba project utilizing Spring Boot framework.
                \item Managed Oracle database operations to ensure seamless data handling.
            \end{itemize}
        } \\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Denka Pharmaceuticals Full-stack Development, Denka} & \hfill \textit{\href{https://www.denka.co.jp/eng/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Engaged in both backend and frontend development for Denka Pharmaceuticals.
                \item Utilized Spring Boot and Thymeleaf for backend and frontend development, respectively.
            \end{itemize}
        } \\
    \end{tabularx}

    \vfill
    \center{\footnotesize Updated On: \today}

\end{document}