\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage[unicode, colorlinks, linkcolor=RoyalBlue, urlcolor=RoyalBlue, citecolor=RoyalBlue]{hyperref}
\definecolor{RoyalBlue}{rgb}{0.25,0.41,0.88}

% Page dimensions
\geometry{
    left=1.27cm,
    right=1.27cm,
    top=1.27cm,
    bottom=1.27cm,
}

% Footer settings
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\footnotesize Updated On: \today}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{15pt} % Add this line to set a suitable value for \footskip

\urlstyle{same}

% Text alignment
\RaggedRight{}
\setlength{\tabcolsep}{0in}


% Section title formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\LARGE
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\subsection}{
    \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}

% Custom commands
\newcommand{\resumeItem}[1]{\item[$\bullet$] \small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubheading}[5]{
    \vspace{-1pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{#4}{#1}} & #2 \\
    \textit{\small#3} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\researchItem}[2]{%
    \resumeItem{\hangindent=1.5em \hangafter=1 \justifying {#1}\\ \textit{#2}}%
}


% CV Start
\begin{document}
    \thispagestyle{empty}

% Title
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textsc{\LARGE Md. Mosfikur Rahman} & \\
    Modhumoti, Sector-18 & Mobile: +880 1797-554948 \\
    Uttara, Dhaka & Portfolio: \href{https://mdmosfikurrahman.github.io/}{mdmosfikurrahman.github.io} \\
    Bangladesh & Email: \href{mailto:mdmosfikurrahman.cse@gmail.com}{mdmosfikurrahman.cse@gmail.com} \\
    \end{tabular*}

% Education
    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {Daffodil International University}{Dhaka, Bangladesh}
    {Bachelor of Science in Computer Science and Engineering; CGPA: \textbf{3.83}}{https://daffodilvarsity.edu.bd/}{Jan. 2018 -- Dec. 2021}
    \resumeSubheading
    {Adam Mickiewicz University}{Poznań, Poland}
    {Erasmus+ Exchange Program in Computer Science; Completed \textbf{6 ECTS}}{https://amu.edu.pl/en}{Mar. 2021 -- Aug. 2021}
    \resumeSubHeadingListEnd

% Experience
    \section{Experience \normalsize{(4+ years)}}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Akij iBOS Ltd.}{Dhaka, Bangladesh}
    {Software Engineer L-II}{https://ibos.io/}{Nov. 2024 – Present}
    \resumeItemListStart
    \resumeItem{Owned end-to-end architecture for OTA Domain, covering supplier configuration, pricing rules, and workflows.}
    \resumeItem{Designed and implemented a rule-based engine for context-aware decision making and dynamic evaluation.}
    \resumeItem{Led backend design for supplier orchestration and aggregated response generation.}
    \resumeItem{Worked with .NET, Node.js, and React while gaining hands-on experience in Docker and deployment workflows.}
    \resumeItem{Defined service boundaries and domain models to ensure scalability and maintainability.}
    \resumeItemListEnd

    \resumeSubheading
    {REVE Systems Ltd.}{Dhaka, Bangladesh}
    {Software Engineer}{https://www.revesoft.com/}{Jul. 2023 – Oct. 2024}
    \resumeItemListStart
    \resumeItem{Developed full-stack applications using Spring Boot, Thymeleaf, React, and Oracle DB in a team environment.}
    \resumeItem{Improved system throughput by 25\% through optimized data access and query performance tuning.}
    \resumeItem{Implemented secure authentication and authorization using OAuth2 and Spring Security.}
    \resumeItemListEnd

    \resumeSubheading
    {BJIT Group}{Dhaka, Bangladesh}
    {Software Engineer (Backend – GraphQL BFF)}{https://bjitgroup.com/}{Apr. 2022 – Jun. 2023}
    \resumeItemListStart
    \resumeItem{Developed GraphQL-based Backend for Frontend (BFF) services using Java and Spring Boot.}
    \resumeItem{Implemented efficient resolver logic, schema stitching, and batching for optimized nested queries.}
    \resumeItem{Optimized database interactions to improve performance and scalability of backend services.}
    \resumeItem{Contributed to reusable service patterns and internal tooling for consistent GraphQL schema design.}
    \resumeItemListEnd


% \resumeSubheading
% {Daffodil International University}{Dhaka, Bangladesh}
% {Teaching Assistant, Dept. of CSE}{https://daffodilvarsity.edu.bd/}{Jun. 2020 – Apr. 2022}
% \resumeItemListStart
% \resumeItem{Assisted in teaching OOP and Data Structures to 150+ students.}
% \resumeItem{Led labs and lectures; designed assignments and practice materials.}
% \resumeItem{Provided mentorship and academic support to students.}
% \resumeItemListEnd

    \resumeSubHeadingListEnd

% Projects
    \section{Projects}
    \resumeSubHeadingListStart

    \resumeSubheading
    {OTA Backend System}{}
    {Akij iBOS Ltd.}{https://ibos.io/}{}
    \resumeItemListStart
    \resumeItem{Owned end-to-end architecture for OTA Domain, covering booking flows, supplier integration, and workflows.}
    \resumeItem{Defined system modules, service boundaries, and interaction patterns for a scalable backend system.}
    \resumeItem{Designed service interfaces, data models, and integration strategies across multiple domain components.}
    \resumeItemListEnd

    \resumeSubheading
    {TrackForce}{}
    {Akij iBOS Ltd.}{https://app.trackforce.io/}{}
    \resumeItemListStart
    \resumeItem{Developed REST APIs for real-time tracking of personnel and shipment.}
    \resumeItem{Integrated SQL-based reporting to improve analytics for field teams.}
    \resumeItem{Enhanced code testability via refactored legacy logic and unit test support.}
    \resumeItemListEnd

    \resumeSubheading
    {Customs Bond Management System}{}
    {REVE Systems Ltd.}{https://cusbond.gov.bd/}{}
    \resumeItemListStart
    \resumeItem{Worked on Legal Case and UD (Utilization Declaration) modules.}
    \resumeItem{Built BGMEA/BKMEA DB sync for garment export compliance.}
    \resumeItemListEnd

    \resumeSubheading
    {Rakuten Echiba Backend}{}
    {BJIT Group}{https://www.rakuten.co.jp/}{}
    \resumeItemListStart
    \resumeItem{Designed GraphQL BFF for e-commerce modules including product and order systems.}
    \resumeItem{Reduced query latency by optimizing resolver logic and database join paths.}
    \resumeItem{Contributed to internal tooling and reusable service patterns for consistent GraphQL schema design.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

% Programming Skills
    \section{Programming Skills}
    \resumeSubHeadingListStart
    \item{
        \textbf{Languages:} Java, C\#, JavaScript, SQL, Python \\
        \textbf{Backend:} Spring Boot, .NET, Node.js, Spring Security, JPA/JDBC, GraphQL \\
        \textbf{Frontend:} React (integration level), Thymeleaf \\
        \textbf{Architecture:} Microservices, REST, API Design, Modular Monolith \\
        \textbf{Databases:} Oracle SQL, PostgreSQL, SQL Server, MySQL \\
        \textbf{Tools:} Docker, CI/CD, Git \\
        \textbf{Technologies:} OAuth2, JWT, Camunda, Drools \\
        \textbf{Concepts:} OOP, Design Patterns, Query Optimization, Secure APIs \\
        \textbf{Operating Systems:} Linux/Unix
    }
    \resumeSubHeadingListEnd


    \section{Research \& Publications}

    \subsection{Journals}
    \resumeItemListStart
    \researchItem
    {Impact of COVID-19 on mental health: A quantitative analysis of anxiety and depression based on regular life and internet use}
    {Current Research in Behavioral Sciences, 2021, 2, 100037}
    \researchItem
    {COVID-19 and Bangladesh: Situation report, comparative analysis, and case study}
    {Current Research in Behavioral Sciences, 2021, 2, 100034}
    \researchItem
    {Impactful e-learning framework: A new hybrid form of education}
    {Current Research in Behavioral Sciences, 2021, 2, 100038}
    \resumeItemListEnd

    \subsection{Conferences}
    \resumeItemListStart
    \researchItem
    {Future City of Bangladesh: IoT Based Autonomous Smart Sewerage and Hazard Condition Sharing System}
    {IEEE WIECON-ECE, 2020}
    \researchItem
    {Cyber Security Intruder Detection Using Deep Learning Approach}
    {Springer: Info. Systems \& Mgmt. Science, 2023}
    \researchItem
    {A New Chaotic-Based Analysis of Data Encryption and Decryption}
    {Springer: Advances in Data Science and AI, 2023}
    \researchItem
    {Machine Learning-Based Prediction of COVID-19: A Robust Approach for Early Diagnosis and Treatment}
    {Springer: Trends in Computational and Cognitive Engineering, 2024}
    \resumeItemListEnd


    \section{Extra-curricular Activities}
    \resumeItemListStart
    \researchItem{\textbf{Conference Speaker}}{Delivered a technical session at the 10th IEEE International Women in Engineering (WIE) Conference on Electrical and Computer Engineering 2024 (IEEE WIECON-ECE 2024).}
    \researchItem{\textbf{Guest Speaker}}{Presented a talk on “How to Get Started: Undergraduate Research Journey” organized by the Computer \& Programming Club, Daffodil International University.}
    \researchItem{\textbf{Vice President, Research \& Career Wing}}{Led mentorship programs, research workshops, and career initiatives at the Computer \& Programming Club, Daffodil International University (2021).}
    \researchItem{\textbf{Technical Lead, “Take Off – 2020”}}{Managed technical operations and project logistics for the university-wide tech event.}
    \researchItem{\textbf{Organizing Member, “Take Off – 2019”}} {Contributed to event planning and programming contest organization for the annual tech competition.}
    \resumeItemListEnd

\end{document}