\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}

\usepackage{enumitem}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear,sorting=ynt, maxbibnames=10]{biblatex}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\setlength\bibitemsep{1em}

\usepackage{fontawesome5}

\newenvironment{jobshort}[2]
{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & #2 \\[3.75pt]
    \end{tabularx}
    }
    {
}

\newenvironment{joblong}[2]
{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=\textbullet]
        }
        {
        \end{itemize}
    \end{minipage}
}

\begin{document}

    \pagestyle{plain}

    \begin{tabularx}{\linewidth}{@{} C @{}}
        \Huge{Md. Mosfikur Rahman} \\[7.5pt]
        \href{https://github.com/mdmosfikurrahman}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \
        \href{https://linkedin.com/in/mdmosfikurrahman}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \
        \href{https://mdmosfikurrahman.github.io}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \
        \href{mailto:mdmosfikurrahman.cse@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ mdmosfikurrahman.cse@gmail.com} \ $|$ \
        \href{tel:+8801332512922}{\raisebox{-0.05\height}\faMobile \ +8801332512922} \\
    \end{tabularx}


    \section{\textbf{Career Objective}}
    Proactive software engineer with a strong Java background, specializing in scalable application development within
    cross-functional teams. Experienced in Spring Boot, Thymeleaf, and proficient in Python, HTML, CSS, and JavaScript, I am
    eager to leverage my analytical skills in algorithm design and REST API integration to drive innovation and growth in a
    forward-looking organization.


    \section{\textbf{Work Experiences}}

    \begin{joblong}{Software Engineer, REVE Systems Ltd.}{July 2023 - Present}
        \item Develop and implement scalable Java applications using advanced design patterns.
        \item Optimize data structures in Oracle DB for efficient storage and retrieval.
        \item Research and integrate new tools, libraries, APIs, and frameworks for enhanced performance.
    \end{joblong}

    \begin{joblong}{Software Engineer, BJIT Group}{April 2022 - June 2023}
        \item Implement JavaEE back-end/API using REST, SOAP, Spring, and microservices.
        \item Build enterprise apps using modern Java web frameworks and Thymeleaf.
        \item Create fundamental design documents, including API specifications and UMLs.
    \end{joblong}

    \begin{joblong}{Trainee Software Engineer, BJIT Group}{October 2021 - March 2022}
        \item Acquired foundational knowledge in software engineering through structured training.
        \item Assisted in coding, debugging, and testing while learning industry best practices.
        \item Developed skills in JavaEE, REST, SOAP, Spring, and front-end technologies.
    \end{joblong}


    \section{\textbf{Skills}}
    \begin{tabularx}{\linewidth}{@{}l X@{}}
        Core Skills           & \normalsize{OOP, REST API, SOAP, Micro-services, Data Structures, UML, Code Review} \\
        Programming Languages & \normalsize{Java, JavaScript, Python}                                               \\
        Frameworks            & \normalsize{Spring Boot, Spring Batch, Bootstrap, Thymeleaf, React JS}              \\
        Technical Tools       & \normalsize{Git, Postman, IntelliJ IDEA, DataGrip}                                  \\
        Database Expertise    & \normalsize{Oracle, MySQL, MongoDB, Spiral DB}                                      \\
    \end{tabularx}


    \section{\textbf{Education}}
    \begin{tabularx}{\linewidth}{@{}l X@{}}
        2021 & Bachelor of Science (B.Sc.) in Computer Science and Engineering \newline \textbf{Daffodil International University, Bangladesh} \hfill (CGPA: 3.83/4.00) \\

        2021 & Exchange Program in Computer Science and Engineering \newline \textbf{Adam Mickiewicz University, Poland} \hfill (Passed with 80\% Marks)                \\

        2016 & Higher Secondary School Certificate \newline \textbf{Major General Mahmudul Hasan Adarsha College, Tangail} \hfill (GPA: 4.67/5.00)                      \\

        2014 & Secondary School Certificate \newline \textbf{Police Lines Adarsha High School, Tangail} \hfill (GPA: 5.00/5.00)                                         \\
    \end{tabularx}


    \section{\textbf{Projects}}
    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Customs Bond Management System, NBR} & \hfill \textit{\href{https://cusbond.gov.bd/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Held key roles across various modules of the CBMS project for the National Board of Revenue (NBR).
                \item Acted as the module owner including Legal and Case Information System, Utilization Declaration System.
                \item Implemented BGMEA and BKMEA Database integration for Utilization Declaration.
                \item Employed a diverse tech stack comprising Spring Boot, Thymeleaf, and Oracle DB for project execution.
            \end{itemize}
        } \\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Rakuten Echiba Backend Development, Rakuten} & \hfill \textit{\href{https://www.rakuten.co.jp/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Solely focused on backend development for the Rakuten Echiba project utilizing Spring Boot framework.
                \item Managed Oracle database operations to ensure seamless data handling.
                \item Led the implementation of a custom framework tailored to meet project-specific requirements.
            \end{itemize}
        } \\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Denka Pharmaceuticals Full-stack Development, Denka} & \hfill \textit{\href{https://www.denka.co.jp/eng/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Engaged in both backend and frontend development for Denka Pharmaceuticals.
                \item Utilized Spring Boot and Thymeleaf for backend and frontend development, respectively.
                \item Contributed to frontend enhancements using React JS.
                \item Managed data storage and retrieval using MySQL database.
            \end{itemize}
        } \\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
        \textbf{Mochida Pharmaceuticals Backend Development, Mochida} & \hfill \textit{\href{https://www.mochida.co.jp/english/}{Link to Demo}} \\[3.75pt]
        \multicolumn{2}{@{}X@{}}{%
            Responsibilities:
            \begin{itemize}[leftmargin=*]
                \item Developed backend functionalities for Mochida Pharmaceuticals using Spring Boot and Spring Batch.
                \item Implemented a unique database solution named Spiral DB to optimize data management processes.
            \end{itemize}
        } \\
    \end{tabularx}


    \section{\textbf{References}}
    \begin{tabularx}{\linewidth}{@{}l X@{}}

        \textbf{Anisuzzaman Rubel}   & Consultant \textendash Enterprise Integrator, Aspire to Innovate (a2i), \newline ICT Division, Dhaka, Bangladesh \\
        & Contact: +880 1906-994487                                                                                        \\
        & Email: \href{mailto:anis.zaman@a2i.gov.bd}{anis.zaman@a2i.gov.bd} \\[3.75pt]

        \textbf{Md. Minhajur Rahman} & Senior General Manager, ENT\textendash4, Engineering Division, \newline BJIT Group, Dhaka, Bangladesh            \\
        & Contact: +880 1816-292692                                                                                        \\
        & Email: \href{mailto:minhajur.rahman@bjitgroup.com}{minhajur.rahman@bjitgroup.com} \\[3.75pt]
    \end{tabularx}


    \vfill
    \center{\footnotesize Updated On: \today}

\end{document}